Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

The part of the paper from this point onwards until the appendix will be devoted to proving the above lemma. This is the most challenging step in settling the general $k$-SJ problem optimally, as we will see in Appendix~\ref{app:ksj}, where we will prove Theorems~\ref{thm:main-recur} and \ref{thm:main-alg} based on Lemma~\ref{lmm:hv}.

@@

We conclude that $\J_1$ (the set of type-1 result tuples) can be computed in $F_{k-2}(n, \out) + O(n \log n +  k \cdot \out)$ time.

@@

We conclude that $\J_1$ (the set of type-1 result tuples) can be computed in $F_{k-2}(n, \out) + O(n \log n +  k \cdot \out)$ time.

@@

\section{Solving the $k$-SJ Problem} \label{app:ksj}

>>>>

The part of the paper from this point till the end of Section~\ref{sec:hv:type2} will be devoted to proving the above lemma. This is the most challenging step in settling the general $k$-SJ problem optimally, as we will see in Appendix~\ref{sec:ksj}, where we will prove Theorems~\ref{thm:main-recur} and \ref{thm:main-alg} based on Lemma~\ref{lmm:hv}.

@@

We conclude that $\J_1$ --- the set of type-1 result tuples --- can be computed in $F_{k-2}(n, \out) + O(n \log n +  k \cdot \out)$ time.

@@

We conclude that $\J_2$ --- the set of type-2 result tuples $(r_1, ..., r_{k-2},$ $h, v)$ where $r_{k-2}$ covers the left endpoint of $h$ --- can be computed in $F_{k-1}(n, \out) + O(n \log n +  k \cdot \out)$ time. Remember that, to generate the entire type-2 result, we need to repeat the algorithm $4(k-2)$ times (one for each sub-type). The total running time is therefore $O(k) \cdot (F_{k-1}(n, \out) + n \log n +  k \cdot \out)$, as claimed in Lemma~\ref{lmm:hv}.

\section{Settling $k$-SJ} \label{sec:ksj}

@@
